---
title: "Analysis_Creativity_Experiment"
output:
  html_document: default
  pdf_document: default
date: "2025-07-09"
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# Clear all ---------------------------------------------------------------
rm(list=ls())

# Install and load required packages 
req <- substitute(require(x, character.only = TRUE))
libs <- c("psych", "dplyr", "skimr", "tidyverse", "tidyr", "ggplot2", "lme4", "lmerTest", "emmeans", "knitr", "gridExtra", "scales", "here", "ggh4x", "fmsb", "stargazer", "grid", "apaTables")
sapply(libs, function(x) eval(req) || {install.packages(x, dependencies = T); eval(req)})




# Global color palette -----------------------------------------------------
# Discrete palette to be used consistently across all ggplot2 plots
ac_palette <- c(
  "#7A9E7E", # Sage Green
  "#4F6D7A", # Slate Blue
  "#5DA9A8", # Muted Teal
  "#A398B3", # Dusty Lavender
  "#D9CFC1", # Warm Sand
  "#4A4A4A"  # Charcoal
)

# Make the palette the default for discrete colour/fill scales
scale_colour_discrete <- function(...) ggplot2::scale_colour_manual(..., values = ac_palette)
scale_color_discrete   <- scale_colour_discrete
scale_fill_discrete    <- function(...) ggplot2::scale_fill_manual(..., values = ac_palette)

# STANDARDIZED BOT ORDER FOR ALL GRAPHICS: feedback, suggestion, improvement, vanilla, control
# (Question-mode, Suggestion-mode, Model-led, Vanilla, Control)

# Global bot-type label map (two-line variants for readability)
label_map <- c(
  control     = "Control",
  vanilla     = "Vanilla",
  feedback    = "Question-Mode",
  improvement = "Model-Led",
  suggestion  = "Suggestion-Mode"
)

# Boxplot-specific label map with line breaks to prevent overlapping
boxplot_label_map <- c(
  control     = "Control",
  vanilla     = "Vanilla",
  feedback    = "Question-\nMode",
  improvement = "Model-\nLed",
  suggestion  = "Suggestion-\nMode"
)

# Global color palette for bot types
bot_colors <- c(
  vanilla     = "#A398B3", # Dusty Lavender
  feedback    = "#4F6D7A", # Slate Blue
  improvement = "#5DA9A8", # Muted Teal
  suggestion  = "#7A9E7E", # Sage Green
  control     = "#D9CFC1"  # Warm Sand
)


# Set project root directory using here package for reproducible paths
library(here)
project_root <- here::here()

# Set working directory to project root
knitr::opts_knit$set(root.dir = project_root)

# Helper path builders using explicit project root
data_path <- function(...) file.path(project_root, "analysis", "Data", ...)
fig_path  <- function(...) file.path(project_root, "analysis", "Figures", ...)
code_path <- function(...) file.path(project_root, "analysis", "Code", ...)
analysis_path <- function(...) file.path(project_root, "analysis", ...)
```


#Overview 
```{r, echo=FALSE}
data_clean <- read.csv(data_path("data_clean.csv"))
elaboration_data <- read.csv2 (data_path("Elaboration_analysis.csv"))
dim(data_clean)         # Dimensions of the data frame.             
head(data_clean,10)     # Shows first n rows.                    
tail(data_clean,10)   # Shows last n rows.                  
str(data_clean)           # Displays the structure of an object.    
summary(data_clean)   # Displays summary statistics.            
colnames(data_clean)    # Column names of an object.            
skim(data_clean) #Skim through the data

```

#Group Comparisons
```{r}
# Calculate group means and SDs for all variables
data_group <- data_clean %>%
  group_by(bot_type) %>%
  summarise(
    # Variables available to ALL participants
    Creative_Self_Efficacy_mean = mean(Creative_Self_Efficacy, na.rm = TRUE),
    Creative_Self_Efficacy_sd = sd(Creative_Self_Efficacy, na.rm = TRUE),
    
    Propensity_to_Trust_Technology_mean = mean(Propensity_to_Trust_Technology, na.rm = TRUE),
    Propensity_to_Trust_Technology_sd = sd(Propensity_to_Trust_Technology, na.rm = TRUE),
    
    # NASA-TLX (if available to all)
    NASA_TLX_mean = mean(rowMeans(select(cur_data(), starts_with("tlx")), na.rm = TRUE), na.rm = TRUE),
    NASA_TLX_sd = sd(rowMeans(select(cur_data(), starts_with("tlx")), na.rm = TRUE), na.rm = TRUE),
    
    # UX-related constructs (only for chatbot users, will be NA for control)
    Perceived_Technology_Agency_mean = mean(Perceived_Technology_Agency, na.rm = TRUE),
    Perceived_Technology_Agency_sd = sd(Perceived_Technology_Agency, na.rm = TRUE),
    
    Performance_Expectancy_mean = mean(Performance_Expectancy, na.rm = TRUE),
    Performance_Expectancy_sd = sd(Performance_Expectancy, na.rm = TRUE),
    
    Effort_Expectancy_mean = mean(Effort_Expectancy, na.rm = TRUE),
    Effort_Expectancy_sd = sd(Effort_Expectancy, na.rm = TRUE),
    
    Hedonic_Motivation_mean = mean(Hedonic_Motivation, na.rm = TRUE),
    Hedonic_Motivation_sd = sd(Hedonic_Motivation, na.rm = TRUE),
    
    Perceived_Ownership_mean = mean(Perceived_Ownership, na.rm = TRUE),
    Perceived_Ownership_sd = sd(Perceived_Ownership, na.rm = TRUE),
    
    AI_experience_mean = mean(ai1, na.rm = TRUE),
    AI_experience_sd = sd(ai1, na.rm = TRUE),
    
    IdeaQuality_mean = mean(Idea_quality, na.rm = TRUE),
    IdeaQuality_sd = sd(Idea_quality, na.rm = TRUE),
    
    #Embeddings based on refined ideas
    refined_div_allideas_mean = mean(refined_div_allideas, na.rm = TRUE),
    refined_div_allideas_sd = sd(refined_div_allideas, na.rm = TRUE),
    refined_div_condition_mean = mean(refined_div_condition, na.rm = TRUE),
    refined_div_condition_sd = sd(refined_div_condition, na.rm = TRUE),
    
    #Embeddings based on initial ideas
    ideas_div_allideas_mean = mean(idea_div_allideas, na.rm = TRUE),
    ideas_div_allideas_sd = sd(idea_div_allideas, na.rm = TRUE),
    ideas_div_condition_mean = mean(idea_div_condition, na.rm = TRUE),
    ideas_div_condition_sd = sd(idea_div_condition, na.rm = TRUE),
    

    Count_Observations = n()
  ) %>%
  ungroup()

# View the grouped data
print(data_group)

write.csv(data_group, data_path("data_group_summary.csv"), row.names = FALSE)
```

#Correlation Matrix
```{r}
# Create correlation matrix with your study variables
correlation_matrix <- data_clean %>%
  dplyr::select(c(
    # Questionnaire constructs
    Idea_quality,
    Perceived_Ownership,
    refined_div_condition,
    Creative_Self_Efficacy,
    Propensity_to_Trust_Technology,
    NASA_TLX,
    Perceived_Technology_Agency,
    Performance_Expectancy,
    Effort_Expectancy,
    Hedonic_Motivation,
    LLM_experience,
    Age,
    total_study_time_seconds
  ))

# Create custom variable names for display
var_names <- c(
  "1. Idea Quality",
  "2. Perceived Ownership", 
  "3. Refined Sim Condition Ideas",
  "4. Creative Self-Efficacy",
  "5. Propensity to Trust Technology",
  "6. NASA TLX",
  "7. Perceived Technology Agency",
  "8. Performance Expectancy",
  "9. Effort Expectancy",
  "10. Hedonic Motivation",
  "11. LLM Experience",
  "12. Age",
  "13. Total Study Time (Seconds)"
)

# Calculate correlations with significance tests
cor_result <- corr.test(correlation_matrix, use = "complete")
cor_matrix <- cor_result$r
p_matrix <- cor_result$p

# Create significance indicators
sig_matrix <- ifelse(p_matrix < 0.01, "**", 
                    ifelse(p_matrix < 0.05, "*", ""))

# Format correlation matrix for display
cor_display <- cor_matrix
diag(cor_display) <- NA  # Remove diagonal
cor_display[lower.tri(cor_display)] <- NA  # Remove lower triangle

# Create formatted correlation strings
cor_formatted <- matrix("", nrow = nrow(cor_matrix), ncol = ncol(cor_matrix))
for(i in seq_len(nrow(cor_matrix))) {
  for(j in seq_len(ncol(cor_matrix))) {
    if(!is.na(cor_display[i,j])) {
      cor_formatted[i,j] <- paste0(sprintf("%.2f", cor_matrix[i,j]), sig_matrix[i,j])
    } else if(i == j) {
      cor_formatted[i,j] <- "---"
    }
  }
}

# Set row and column names
rownames(cor_formatted) <- var_names
colnames(cor_formatted) <- seq_len(ncol(cor_matrix))

# Calculate descriptive statistics
means <- sapply(correlation_matrix, mean, na.rm = TRUE)
sds <- sapply(correlation_matrix, sd, na.rm = TRUE)

# Create descriptive stats table
desc_stats <- data.frame(
  Variable = var_names,
  M = sprintf("%.2f", means),
  SD = sprintf("%.2f", sds),
  stringsAsFactors = FALSE
)

# APA-style correlation table (display only, no file saved)
# Use descriptive variable names as column headers for the APA table
colnames(correlation_matrix) <- var_names

apaTables::apa.cor.table(
  correlation_matrix,
  table.number = NA,
  filename = "Correlations"
)

# Note: apaTables already includes M and SD in the correlation table; no file is saved
```

# Reliability Analysis
# Creative Self-Efficacy
```{r}
CreativeSelfEfficacy <- data_clean %>%
  dplyr::select(., c(cse1, cse2, cse3))
alpha_CreativeSelfEfficacy <- psych::alpha(CreativeSelfEfficacy, check.keys = TRUE)
print(alpha_CreativeSelfEfficacy)
```

# Perceived Technology Agency
```{r}
PerceivedTechnologyAgency <- data_clean %>%
  dplyr::select(., c(pta1, pta2, pta3, pta4, pta5))
alpha_PerceivedTechnologyAgency <- psych::alpha(PerceivedTechnologyAgency, check.keys = TRUE)
print(alpha_PerceivedTechnologyAgency)
```

# NASA-TLX
```{r}
NASATLX <- data_clean %>%
  dplyr::select(., c(tlx1, tlx2))

# Inter-item Pearson correlation (2-item scale)
nasatlx_test <- cor.test(NASATLX$tlx1, NASATLX$tlx2, method = "pearson")
print(nasatlx_test)
```

# Performance Expectancy
```{r}
PerformanceExpectancy <- data_clean %>%
  dplyr::select(., c(pe1, pe2, pe3))
alpha_PerformanceExpectancy <- psych::alpha(PerformanceExpectancy, check.keys = TRUE)
print(alpha_PerformanceExpectancy)
```

# Effort Expectancy
```{r}
EffortExpectancy <- data_clean %>%
  dplyr::select(., c(ee1, ee2, ee3, ee4))
alpha_EffortExpectancy <- psych::alpha(EffortExpectancy, check.keys = TRUE)
print(alpha_EffortExpectancy)
```

# Hedonic Motivation
```{r}
HedonicMotivation <- data_clean %>%
  dplyr::select(., c(hm1, hm2, hm3))
alpha_HedonicMotivation <- psych::alpha(HedonicMotivation, check.keys = TRUE)
print(alpha_HedonicMotivation)
```

# Propensity to Trust Technology
```{r}
PropensityTrustTechnology <- data_clean %>%
  dplyr::select(., c(ptt1, ptt2_rev, ptt3, ptt4, ptt5, ptt6))
alpha_PropensityTrustTechnology <- psych::alpha(PropensityTrustTechnology, check.keys = TRUE)
print(alpha_PropensityTrustTechnology)
```

# Perceived Ownership
```{r}
PerceivedOwnership <- data_clean %>%
  dplyr::select(., c(io1, io2, io3, io4, io5))
alpha_PerceivedOwnership <- psych::alpha(PerceivedOwnership, check.keys = TRUE)
print(alpha_PerceivedOwnership)
```

# Reliability Summary
```{r}
# Cronbach's alpha for multi-item scales (excluding 2-item NASA-TLX)
reliability_summary <- data.frame(
  Scale = c("Creative Self-Efficacy", "Perceived Technology Agency",
           "Performance Expectancy", "Effort Expectancy", "Hedonic Motivation",
           "Propensity to Trust Technology", "Perceived Ownership"),
  Cronbachs_Alpha = c(
    alpha_CreativeSelfEfficacy$total$raw_alpha,
    alpha_PerceivedTechnologyAgency$total$raw_alpha,
    alpha_PerformanceExpectancy$total$raw_alpha,
    alpha_EffortExpectancy$total$raw_alpha,
    alpha_HedonicMotivation$total$raw_alpha,
    alpha_PropensityTrustTechnology$total$raw_alpha,
    alpha_PerceivedOwnership$total$raw_alpha
  ),
  Items = c(3, 5, 3, 4, 3, 6, 5)
)

knitr::kable(reliability_summary, digits = 3, caption = "Cronbach's Alpha for Multi-item Scales")

# Inter-item Pearson r for NASA-TLX (2 items)
nasatlx_test <- cor.test(data_clean$tlx1, data_clean$tlx2, method = "pearson")
nasatlx_reliability <- data.frame(
  Scale = "NASA-TLX (2 items)",
  Pearson_r = round(unname(nasatlx_test$estimate), 3),
  CI_low = round(nasatlx_test$conf.int[1], 3),
  CI_high = round(nasatlx_test$conf.int[2], 3),
  p_value = signif(nasatlx_test$p.value, 3)
)
knitr::kable(nasatlx_reliability, digits = 3, caption = "Inter-item Pearson correlation for NASA-TLX")
```


#Rater reliability: ICC
```{r}
# More comprehensive analysis
rater_data <- data.frame(
  Rater1 = as.numeric(data_clean$Rater1),
  Rater2 = as.numeric(data_clean$Rater2),
  Rater3 = as.numeric(data_clean$Rater3),
  Rater4 = as.numeric(data_clean$Rater4)
)

# Calculate ICC
icc_result <- ICC(rater_data)
print(icc_result)
```

#H1: Idea quality significantly improves when participants interact with (a) a suggestion model LLM, (b) a question model LLM, (c) a model-led LLM or (d) a vanilla LLM compared to a control condition without LLM support.
```{r}
data_clean$bot_type <- factor(data_clean$bot_type,
                            levels = c("feedback", "suggestion", "improvement", "vanilla", "control"))
levels(data_clean$bot_type)

# Fit the linear model
quality_model <- lm(Average ~ bot_type, data = data_clean)

# Summary and ANOVA
summary(quality_model)
anova(quality_model)

# Estimate marginal means
quality_emm <- emmeans(quality_model, specs = ~ bot_type)

# Define contrasts for hypothesis testing
# Contrasts: feedback (Question-mode), suggestion (Suggestion-mode), improvement (Model-led), vanilla, control
contrast_list <- list(
  H1a = c(1,  0,  0,  0, -1),  
  H1b = c(0, 1,  0,  0, -1),
  H1c = c(0,  0,  1,  0, -1),
  H1d = c( 0, 0,  0,  1, -1)
)

# Get Holm-adjusted p-values
contrast_adjusted <- contrast(quality_emm, method = contrast_list, adjust = "holm", infer = TRUE, side = ">")
print("Holm-adjusted p-values:")
print(contrast_adjusted)

# Get unadjusted confidence intervals
contrast_unadjusted <- contrast(quality_emm, method = contrast_list, adjust = "none", infer = TRUE, side = ">")
print("Unadjusted confidence intervals:")
print(contrast_unadjusted)

# Calculate effect sizes (Cohen's d)
# Get the residual standard deviation from the model
pooled_sd <- sigma(quality_model)

# Get contrast results
contrast_results <- contrast(quality_emm, method = contrast_list, adjust = "holm")


eff_size(quality_emm, method = contrast_list, sigma = pooled_sd, edf = df.residual(quality_model))
```

#H2:The diversity of the idea pool is higher when participants interact with a 
question mode LLM compared to (a) a model-led LLM and (b) a vanilla LLM.

#H3:The diversity of the idea pool is higher when participants interact with a 
suggestion mode LLM compared to (a) a model-led LLM and (b) a vanilla LLM.

```{r}
data_clean$bot_type <- factor(data_clean$bot_type,
                            levels = c("feedback", "suggestion", "improvement", "vanilla", "control"))
levels(data_clean$bot_type)

# Fit the linear model
DIV_model <- lm(refined_div_condition ~ bot_type, data = data_clean)

# Summary and ANOVA
summary(DIV_model)
anova(DIV_model)

# Estimate marginal means
SIM_emm <- emmeans(DIV_model, specs = ~ bot_type)

# Define contrasts for hypothesis testing
# Contrasts: feedback (Question-mode), suggestion (Suggestion-mode), improvement (Model-led), vanilla, control
contrast_list <- list(
  H2a = c(1,  0,  -1,  0, 0),  
  H2b = c(1, 0,  0,  -1, 0),
  H3a = c(0,  1,  -1,  0, 0),
  H3b = c( 0, 1,  0,  -1, 0)
)

# Get Holm-adjusted p-values
contrast_adjusted <- contrast(SIM_emm, method = contrast_list, adjust = "holm", infer = TRUE, side = ">")
print("Holm-adjusted p-values:")
print(contrast_adjusted)

# Get unadjusted confidence intervals  
contrast_unadjusted <- contrast(SIM_emm, method = contrast_list, adjust = "none", infer = TRUE, side = ">")
print("Unadjusted confidence intervals:")
print(contrast_unadjusted)

# Calculate effect sizes (Cohen's d) for H2 & H3
eff_size(SIM_emm, method = contrast_list, sigma = sigma(DIV_model), edf = df.residual(DIV_model))
```

#H4: The perceived idea ownership is higher when participants interact with a question mode LLM compared to (a) a model-led LLM and (b) a vanilla LLM
#H5: The perceived idea ownership is higher when participants interact with a suggestion mode LLM compared to (a) a model-led LLM and (b) a vanilla LLM 
```{r}
data_clean$bot_type <- factor(data_clean$bot_type,
                            levels = c("feedback", "suggestion", "improvement", "vanilla", "control"))
levels(data_clean$bot_type)

# Fit the linear model
PO_model <- lm(Perceived_Ownership ~ bot_type, data = data_clean)

# Summary and ANOVA
summary(PO_model)
anova(PO_model)

# Estimate marginal means
PO_emm <- emmeans(PO_model, specs = ~ bot_type)

# Define contrasts for hypothesis testing
# Contrasts: feedback (Question-mode), suggestion (Suggestion-mode), improvement (Model-led), vanilla, control
contrast_list <- list(
  H4a = c(1,  0,  -1,  0, 0),  
  H4b = c(1, 0,  0,  -1, 0),
  H5a = c(0,  1,  -1,  0, 0),
  H5b = c(0, 1,  0,  -1, 0)
)

# Get Holm-adjusted p-values
contrast_adjusted <- contrast(PO_emm, method = contrast_list, adjust = "holm", infer = TRUE, side = ">")
print("Holm-adjusted p-values:")
print(contrast_adjusted)

# Get unadjusted confidence intervals  
contrast_unadjusted <- contrast(PO_emm, method = contrast_list, adjust = "none", infer = TRUE, side = ">")
print("Unadjusted confidence intervals:")
print(contrast_unadjusted)

# Calculate effect sizes (Cohen's d) for H4 & H5
eff_size(PO_emm, method = contrast_list, sigma = sigma(PO_model), edf = df.residual(PO_model))
```

#Explorative Analyses
##Elaboration Depth
```{r}
# First, clean and prepare the elaboration data
elaboration_descriptives <- elaboration_data %>%
  rename(participant_id = ID, condition = Condition) %>%
  mutate(
    H_IDEA_Score = as.numeric(H_IDEA_Score),
    participant_id = as.character(participant_id)
  ) %>%
  filter(!is.na(H_IDEA_Score)) %>%
  select(participant_id, condition, H_IDEA_Score)

# Create frequency table with percentages
cat("Häufigkeitstabelle für Elaboration Depth (H_IDEA_Score) nach Bedingungen\n")
cat("=======================================================================\n\n")

# Cross-tabulation: absolute frequencies
freq_table <- table(elaboration_descriptives$condition, elaboration_descriptives$H_IDEA_Score)
cat("Absolute Häufigkeiten:\n")
print(freq_table)

# Cross-tabulation: percentages within conditions (row percentages)
cat("\n\nProzentuale Verteilung innerhalb der Bedingungen (Zeilenprozente):\n")
perc_table_rows <- round(prop.table(freq_table, margin = 1) * 100, 1)
print(perc_table_rows)

# Cross-tabulation: percentages within scores (column percentages) 
cat("\n\nProzentuale Verteilung innerhalb der Scores (Spaltenprozente):\n")
perc_table_cols <- round(prop.table(freq_table, margin = 2) * 100, 1)
print(perc_table_cols)

# Overall percentages
cat("\n\nGesamtprozente:\n")
perc_table_total <- round(prop.table(freq_table) * 100, 1)
print(perc_table_total)

# Summary table with totals
cat("\n\nZusammenfassung mit Gesamtzahlen:\n")
summary_table <- elaboration_descriptives %>%
  group_by(condition) %>%
  summarise(
    Gesamt_n = n(),
    .groups = 'drop'
  )
print(summary_table)

# Create formatted table for publication
kable(perc_table_rows, 
      caption = "Prozentuale Verteilung der H_IDEA_Score innerhalb der Bedingungen",
      digits = 1)
```

## Differences in cognitive load: Human-Led vs. Model-Led & Vanilla
```{r}
data_clean$bot_type <- factor(data_clean$bot_type,
                            levels = c("feedback", "suggestion", "improvement", "vanilla", "control"))
levels(data_clean$bot_type)

# Fit the linear model
NASA_model <- lm(NASA_TLX ~ bot_type, data = data_clean)

# Summary and ANOVA
summary(NASA_model)
anova(NASA_model)

# Estimate marginal means
NASA_emm <- emmeans(NASA_model, specs = ~ bot_type)

# Define contrasts for hypothesis testing
# Contrasts: feedback (Question-mode), suggestion (Suggestion-mode), improvement (Model-led), vanilla, control
contrast_list <- list(
  E1 = c(1,  0,  -1,  0, 0),  
  E2 = c(1, 0,  0,  -1, 0),
  E3 = c(0,  1,  -1,  0, 0),
  E4 = c(0, 1,  0,  -1, 0)
)

# Get Holm-adjusted p-values
contrast_adjusted <- contrast(NASA_emm, method = contrast_list, adjust = "holm", infer = TRUE)
print("Holm-adjusted p-values:")
print(contrast_adjusted)

# Get unadjusted confidence intervals  
contrast_unadjusted <- contrast(NASA_emm, method = contrast_list, adjust = "none", infer = TRUE)
print("Unadjusted confidence intervals:")
print(contrast_unadjusted)

# Calculate effect sizes (Cohen's d)
eff_size(NASA_emm, method = contrast_list, sigma = sigma(NASA_model), edf = df.residual(NASA_model))
```


## Simple regression: NASA-TLX predicting Perceived Idea Ownership
```{r}
# Simple linear regression
ownership_nasa_model <- lm(Perceived_Ownership ~ NASA_TLX, data = data_clean)
summary(ownership_nasa_model)
confint(ownership_nasa_model)

model_std <- lm(scale(Perceived_Ownership) ~ scale(NASA_TLX), data = data_clean)
summary(model_std)
```

# WITHIN-SUBJECT ANALYSIS: Initial vs Refined Ideas by Bot Type
## Descriptives
```{r}
# Prepare data for within-subject analysis with renamed bot types
analysis_data <- data_clean %>%
  filter(bot_type %in% c("feedback", "suggestion", "improvement")) %>%
  select(participant_id, bot_type, 
         initial_diversity = idea_div_condition,
         refined_to_centroid = refined_div_to_initial_centroid) %>%
  filter(!is.na(initial_diversity) & !is.na(refined_to_centroid)) %>%
  mutate(
    # Within-subject change (pre-post difference)
    diversity_change = refined_to_centroid - initial_diversity,
    
    # Rename bot types for better presentation (two-line labels)
    bot_type_renamed = case_when(
      bot_type == "feedback"    ~ "Question-\nmode",
      bot_type == "improvement" ~ "Model-\nled", 
      bot_type == "suggestion"  ~ "Suggestion-\nmode",
      TRUE ~ as.character(bot_type)
    ),
    # Factor levels for renamed labels (display order)
    bot_type_renamed = factor(bot_type_renamed, 
                             levels = c("Question-\nmode", "Suggestion-\nmode", "Model-\nled")),
    
    # Factor levels for original bot_type (analysis order)
    bot_type = factor(bot_type, levels = c("feedback", "suggestion", "improvement"))
  )

print(table(analysis_data$bot_type_renamed))

# Summary statistics by condition (using renamed bot types)
change_summary <- analysis_data %>%
  group_by(bot_type_renamed) %>%
  summarise(
    n = n(),
    mean_initial = mean(initial_diversity, na.rm = TRUE),
    mean_refined_to_centroid = mean(refined_to_centroid, na.rm = TRUE), 
    mean_change = mean(diversity_change, na.rm = TRUE),
    sd_change = sd(diversity_change, na.rm = TRUE),
    .groups = 'drop'
  )

cat("\n=== WITHIN-SUBJECT CHANGE SUMMARY ===\n")
print(change_summary)
```

## Exploratory Mixed-Effects Models: Initial Diversity vs Refined Distance to Centroid
```{r}
lmm_diversity_data <- data_clean %>%
  dplyr::select(
    participant_id,
    bot_type,
    # DV components
    idea_div_condition,
    refined_div_to_initial_centroid,
    # Covariates
    # Keep only NASA-TLX mental effort (tlx2)
    tlx2
  ) %>%
  tidyr::pivot_longer(
    cols = c(idea_div_condition, refined_div_to_initial_centroid),
    names_to = "time",
    values_to = "diversity_score"
  ) %>%
  dplyr::mutate(
    participant_id = factor(participant_id),
    bot_type = factor(as.character(bot_type)),
    time = factor(time,
                  levels = c("idea_div_condition", "refined_div_to_initial_centroid"),
                  labels = c("Initial", "Refined to Centroid"))
  ) %>%
  dplyr::filter(!is.na(bot_type)) %>%
  # Keep only multi-timepoint bot conditions
  dplyr::filter(bot_type %in% c("feedback", "improvement", "suggestion")) %>%
  tidyr::drop_na(diversity_score)

m1 <- lmerTest::lmer(
  diversity_score ~ bot_type * time + (1 | participant_id),
  data = lmm_diversity_data,
  REML = FALSE
)
summary(m1)
anova(m1)

emm_time_by_bot <- emmeans(m1, ~ time | bot_type)
change_by_bot <- contrast(emm_time_by_bot, "revpairwise")  # Refined − Initial per bot
summary(change_by_bot, adjust = "holm", infer = TRUE)


# EMMs for the 3x2 cells
emm_cells <- emmeans(m1, ~ bot_type * time)

# All pairwise differences in CHANGE between bots:
did_all <- contrast(
  emm_cells,
  interaction = list("pairwise", "revpairwise")  # bot diffs × (Refined−Initial)
)

summary(did_all, adjust = "holm", infer = TRUE)   # pairwise change comparisons with multiplicity control
```

# WITHIN-SUBJECT VISUALIZATION: Before-After Plot
```{r}
# Reshape data for before-after plot with renamed bot types
before_after_data <- analysis_data %>%
  pivot_longer(cols = c(initial_diversity, refined_to_centroid),
               names_to = "timepoint", 
               values_to = "diversity") %>%
  mutate(
    timepoint = factor(timepoint, 
                      levels = c("initial_diversity", "refined_to_centroid"),
                      labels = c("Initial Ideas", "Refined Ideas")),
    participant_id = factor(participant_id)
  )

# Calculate means for overlay using renamed bot types
means_data <- before_after_data %>%
  group_by(bot_type_renamed, timepoint) %>%
  summarise(mean_diversity = mean(diversity, na.rm = TRUE), .groups = 'drop')

# Publication-ready before-after plot
p_within_subject <- ggplot(before_after_data, aes(x = timepoint, y = diversity, group = participant_id)) +
  
  # Individual trajectories (light lines)
  geom_line(alpha = 0.2, color = "gray70", size = 0.2) +
  geom_point(alpha = 0.3, size = 0.6, color = "gray70") +
  
  # Mean trajectories (thick lines)
  geom_line(data = means_data, aes(x = timepoint, y = mean_diversity, group = bot_type_renamed, color = bot_type_renamed),
            size = 1.5, inherit.aes = FALSE) +
  geom_point(data = means_data, aes(x = timepoint, y = mean_diversity, color = bot_type_renamed),
             size = 3, inherit.aes = FALSE) +
  
  # Reference line
  geom_hline(yintercept = mean(analysis_data$initial_diversity), 
             linetype = "dashed", alpha = 0.4, color = "black", size = 0.5) +
  
  # Bot colors (use global discrete palette)
  scale_color_discrete(name = "Bot Type") +
  
  # Use facet_grid instead of facet_wrap for better spacing control
  facet_grid(. ~ bot_type_renamed) +
  
  # Clean labels
  labs(
    x = "Idea Stage",
    y = "Diversity Score"
  ) +
  
  # Publication theme
  theme_minimal() +
  theme(
    # Remove titles
    plot.title = element_blank(),
    plot.subtitle = element_blank(),
    plot.caption = element_blank(),
    
    # Facet labels with reduced margins
    strip.text = element_text(size = 11, face = "bold", color = "black",
                             margin = margin(2, 2, 2, 2)),
    strip.background = element_blank(),
    
    # Axis text
    axis.text = element_text(size = 10, color = "black"),
    axis.title = element_text(size = 11, face = "bold", color = "black"),
    
    # Remove legend completely
    legend.position = "none",
    
    # Panel spacing - very tight spacing between panels
    panel.spacing.x = unit(0.01, "lines"),
    panel.spacing.y = unit(0.01, "lines"),
    
    # Grid
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "gray95", size = 0.3),
    
    # Minimal margins to make panels bigger
    plot.margin = margin(5, 5, 5, 5)
  )

print(p_within_subject)

# Save with bigger dimensions to make individual panels larger
# Also save as PDF for LaTeX
ggsave(fig_path("within_subject_change_publication.pdf"), p_within_subject, 
       width = 12, height = 4.5, device = "pdf", bg = "white")
```



#Violin Plot Dependent Variables 
```{r}
idea_quality_col <- "Average"
refined_div_col <- "refined_div_condition"

data_clean <- data_clean %>%
  mutate(
    !!idea_quality_col := as.numeric(!!sym(idea_quality_col)),
    !!refined_div_col := as.numeric(!!sym(refined_div_col)),
    Perceived_Ownership = as.numeric(Perceived_Ownership)
  )

# --- Conditions and approved colors ---
# Standardized order for all graphics: Question-mode, Suggestion-mode, Model-led, Vanilla, Control
desired_levels <- c("feedback", "suggestion", "improvement", "vanilla", "control")
present_levels <- desired_levels[desired_levels %in% unique(as.character(data_clean$bot_type))]

data_clean <- data_clean %>%
  mutate(bot_type = factor(as.character(bot_type), levels = present_levels))


# Pretty labels for bot types (single-line for non-boxplot graphics)
# Note: Using the global label_map defined earlier, no need to redefine



# --- Long data for the three DVs ---
dv_vars <- c(refined_div_col, idea_quality_col, "Perceived_Ownership")
dv_labels <- setNames(
  c("Idea Diversity", "Idea Quality", "Perceived Idea Ownership"),
  dv_vars
)

plot_data <- data_clean %>%
  select(bot_type, all_of(dv_vars)) %>%
  pivot_longer(cols = all_of(dv_vars), names_to = "dv", values_to = "score") %>%
  filter(!is.na(bot_type), !is.na(score)) %>%
  mutate(
    # Limit Perceived Ownership to 0-7 range
    score = ifelse(dv == "Perceived_Ownership", pmin(pmax(score, 0), 7), score),
    dv = factor(dv, levels = dv_vars, labels = dv_labels[dv_vars])
  )

# --- Violin plot (facetted) ---
p_violin <- ggplot(plot_data, aes(x = bot_type, y = score, fill = bot_type)) +
  geom_violin(data = filter(plot_data, dv != "Perceived Idea Ownership"), 
              trim = FALSE, alpha = 0.85, color = NA) +
  geom_violin(data = filter(plot_data, dv == "Perceived Idea Ownership"), 
              trim = TRUE, alpha = 0.85, color = NA) +
  geom_boxplot(width = 0.14, outlier.shape = NA, color = "white", alpha = 0.95) +
  stat_summary(fun = median, geom = "point", shape = 23, size = 2.2, fill = "white") +
  facet_wrap(~ dv, scales = "free_y", ncol = 3) +
  ggh4x::facetted_pos_scales(
    y = list(
      dv == "Perceived Idea Ownership" ~ scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1))
    )
  ) +
  scale_x_discrete(limits = present_levels, labels = boxplot_label_map[present_levels]) +
  scale_fill_manual(values = bot_colors[present_levels],
                    breaks = present_levels,
                    labels = boxplot_label_map[present_levels],
                    limits = present_levels) +
  labs(x = "Bot Type", y = "Score") +
  guides(fill = "none") +
  theme_minimal(base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold"))

print(p_violin)

# Save violin plots
dir.create(here::here("Analysis", "Figures"), showWarnings = FALSE, recursive = TRUE)
# Also save as PDF (vector graphics)
ggsave(
  filename = here::here("Analysis", "Figures", "violin_refinedSim_ideaQuality_ownership_by_condition.pdf"),
  plot = p_violin, width = 12, height = 4.5, device = "pdf", bg = "white", useDingbats = FALSE
)
```


#Violin Plot Cognitive Workload
```{r}
# Custom bot order for TLX violin: Question-mode, Suggestion-mode, Model-led, Vanilla, Control
desired_levels_tlx <- c("feedback", "suggestion", "improvement", "vanilla", "control")
present_levels_tlx <- desired_levels_tlx[desired_levels_tlx %in% unique(as.character(data_clean$bot_type))]

# Prepare data for composite NASA-TLX measure
tlx_data <- data_clean %>%
  dplyr::select(bot_type, NASA_TLX) %>%
  dplyr::filter(!is.na(bot_type), !is.na(NASA_TLX)) %>%
  dplyr::mutate(bot_type = factor(as.character(bot_type), levels = present_levels_tlx))

p_tlx_violin <- ggplot2::ggplot(tlx_data, ggplot2::aes(x = bot_type, y = NASA_TLX, fill = bot_type)) +
  ggplot2::geom_violin(trim = FALSE, alpha = 0.85, color = NA) +
  ggplot2::geom_boxplot(width = 0.14, outlier.shape = NA, color = "white", alpha = 0.95) +
  ggplot2::stat_summary(fun = median, geom = "point", shape = 23, size = 2.2, fill = "white") +
  ggplot2::scale_x_discrete(limits = present_levels_tlx, labels = boxplot_label_map[present_levels_tlx]) +
  ggplot2::scale_fill_manual(values = bot_colors[present_levels_tlx],
                             breaks = present_levels_tlx,
                             labels = boxplot_label_map[present_levels_tlx],
                             limits = present_levels_tlx) +
  ggplot2::labs(x = "Bot Type", y = "Perceived Cognitive Workload") +
  ggplot2::scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  ggplot2::guides(fill = "none") +
  ggplot2::theme_minimal(base_size = 12) +
  ggplot2::theme(panel.grid.minor = ggplot2::element_blank())

print(p_tlx_violin)

# Create bar charts for cognitive workload and creative self-efficacy
# Prepare data for bar charts - calculate means and standard errors
bar_data <- data_clean %>%
  dplyr::filter(!is.na(bot_type)) %>%
  dplyr::mutate(bot_type = factor(as.character(bot_type), levels = present_levels_tlx)) %>%
  dplyr::group_by(bot_type) %>%
  dplyr::summarise(
    NASA_TLX_mean = mean(NASA_TLX, na.rm = TRUE),
    NASA_TLX_se = sd(NASA_TLX, na.rm = TRUE) / sqrt(n()),
    Creative_Self_Efficacy_mean = mean(Creative_Self_Efficacy, na.rm = TRUE),
    Creative_Self_Efficacy_se = sd(Creative_Self_Efficacy, na.rm = TRUE) / sqrt(n()),
    n = n(),
    .groups = 'drop'
  ) %>%
  dplyr::filter(!is.na(bot_type))


# Create cognitive workload bar chart (ACM/CHI publication style)
p_tlx_bar <- ggplot2::ggplot(bar_data, ggplot2::aes(x = bot_type, y = NASA_TLX_mean, fill = bot_type)) +
  ggplot2::geom_col(alpha = 0.8, color = NA, width = 0.7) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin = pmax(0, NASA_TLX_mean - NASA_TLX_se), 
                                      ymax = pmin(100, NASA_TLX_mean + NASA_TLX_se)),
                         width = 0.25, size = 0.6, color = "black") +
  ggplot2::scale_x_discrete(limits = present_levels_tlx, labels = boxplot_label_map[present_levels_tlx]) +
  ggplot2::scale_fill_manual(values = bot_colors[present_levels_tlx],
                             breaks = present_levels_tlx,
                             labels = boxplot_label_map[present_levels_tlx],
                             limits = present_levels_tlx) +
  ggplot2::labs(x = "", y = "Cognitive Workload (0-100)", title = "(a) Perceived Cognitive Workload") +
  ggplot2::scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 25), expand = c(0, 0)) +
  ggplot2::guides(fill = "none") +
  ggplot2::theme_classic(base_size = 10) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(hjust = 0, size = 11, face = "bold", margin = ggplot2::margin(b = 10)),
    axis.title.y = ggplot2::element_text(size = 10, margin = ggplot2::margin(r = 8)),
    axis.text.x = ggplot2::element_text(size = 9, angle = 45, hjust = 1, margin = ggplot2::margin(t = 1)),
    axis.text.y = ggplot2::element_text(size = 9),
    axis.line = ggplot2::element_line(color = "black", size = 0.4),
    axis.ticks = ggplot2::element_line(color = "black", size = 0.4),
    panel.background = ggplot2::element_rect(fill = "white", color = NA),
    plot.background = ggplot2::element_rect(fill = "white", color = NA),
    panel.grid.major.y = ggplot2::element_line(color = "gray95", size = 0.3),
    panel.grid.major.x = ggplot2::element_blank(),
    plot.margin = ggplot2::margin(8, 10, 4, 8)
  )

# Create creative self-efficacy bar chart (ACM/CHI publication style)
p_cse_bar <- ggplot2::ggplot(bar_data, ggplot2::aes(x = bot_type, y = Creative_Self_Efficacy_mean, fill = bot_type)) +
  ggplot2::geom_col(alpha = 0.8, color = NA, width = 0.7) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin = pmax(0, Creative_Self_Efficacy_mean - Creative_Self_Efficacy_se), 
                                      ymax = pmin(7, Creative_Self_Efficacy_mean + Creative_Self_Efficacy_se)),
                         width = 0.25, size = 0.6, color = "black") +
  ggplot2::scale_x_discrete(limits = present_levels_tlx, labels = boxplot_label_map[present_levels_tlx]) +
  ggplot2::scale_fill_manual(values = bot_colors[present_levels_tlx],
                             breaks = present_levels_tlx,
                             labels = boxplot_label_map[present_levels_tlx],
                             limits = present_levels_tlx) +
  ggplot2::labs(x = "", y = "Creative Self-Efficacy (1-7)", title = "(b) Creative Self-Efficacy") +
  ggplot2::scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1), expand = c(0, 0)) +
  ggplot2::guides(fill = "none") +
  ggplot2::theme_classic(base_size = 10) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(hjust = 0, size = 11, face = "bold", margin = ggplot2::margin(b = 10)),
    axis.title.y = ggplot2::element_text(size = 10, margin = ggplot2::margin(r = 8)),
    axis.text.x = ggplot2::element_text(size = 9, angle = 45, hjust = 1, margin = ggplot2::margin(t = 1)),
    axis.text.y = ggplot2::element_text(size = 9),
    axis.line = ggplot2::element_line(color = "black", size = 0.4),
    axis.ticks = ggplot2::element_line(color = "black", size = 0.4),
    panel.background = ggplot2::element_rect(fill = "white", color = NA),
    plot.background = ggplot2::element_rect(fill = "white", color = NA),
    panel.grid.major.y = ggplot2::element_line(color = "gray95", size = 0.3),
    panel.grid.major.x = ggplot2::element_blank(),
    plot.margin = ggplot2::margin(8, 10, 4, 8)
  )

# Combine bar charts side by side with minimal spacing
combined_bar_plot <- gridExtra::grid.arrange(
  p_tlx_bar, p_cse_bar, 
  ncol = 2, 
  heights = unit(3, "in"),
  widths = unit.c(unit(3.5, "in"), unit(3.5, "in"))
)

print(combined_bar_plot)

# Save outputs
dir.create(here::here("Analysis", "Figures"), showWarnings = FALSE, recursive = TRUE)

# Save violin plots
ggplot2::ggsave(
  filename = here::here("Analysis", "Figures", "violin_cognitive_workload_by_condition.pdf"),
  plot = p_tlx_violin, width = 7, height = 4.5, device = "pdf", bg = "white", useDingbats = FALSE
)

# Save bar charts (ACM/CHI publication quality)
ggplot2::ggsave(
  filename = here::here("Analysis", "Figures", "bar_cognitive_workload_creativeSE_by_condition.pdf"),
  plot = combined_bar_plot, width = 7, height = 3.5, device = "pdf", bg = "white", 
  useDingbats = FALSE, units = "in"
)

# Save individual charts for single-column figures if needed
ggplot2::ggsave(
  filename = here::here("Analysis", "Figures", "bar_cognitive_workload_publication.pdf"),
  plot = p_tlx_bar, width = 3.5, height = 3, device = "pdf", bg = "white", 
  useDingbats = FALSE, units = "in"
)
ggplot2::ggsave(
  filename = here::here("Analysis", "Figures", "bar_creative_self_efficacy_publication.pdf"),
  plot = p_cse_bar, width = 3.5, height = 3, device = "pdf", bg = "white", 
  useDingbats = FALSE, units = "in"
)
```


# UX Measures Spider Plot
```{r}
# Ensure figures directory exists
dir.create(fig_path(), showWarnings = FALSE, recursive = TRUE)

# Clean the elaboration data and extract participant_id
elaboration_clean <- elaboration_data %>%
  rename(participant_id = ID, bot_type_elab = Condition) %>%
  mutate(
    H_IDEA_Score = as.numeric(H_IDEA_Score),
    participant_id = as.character(participant_id)
  ) %>%
  select(participant_id, bot_type_elab, H_IDEA_Score) %>%
  filter(!is.na(H_IDEA_Score))

cat("Elaboration data loaded. Rows:", nrow(elaboration_clean), "\n")
cat("H_IDEA_Score range:", range(elaboration_clean$H_IDEA_Score, na.rm = TRUE), "\n")

# Define the UX measures we want to include in the spider plot
ux_measures <- c(
  "Performance_Expectancy", 
  "Effort_Expectancy",
  "Hedonic_Motivation",
  "Perceived_Ownership",
  "Creative_Self_Efficacy",  # Added creative self-efficacy
  "Mental_Load",  # Combined mental demand and mental effort
  "Elaboration_Depth"  # From H_IDEA_Score
)

# Create readable labels for the spider plot
ux_measure_labels <- c(
  "Performance\nExpectancy",
  "Effort\nExpectancy", 
  "Hedonic\nMotivation",
  "Perceived\nOwnership",
  "Creative\nSelf-Efficacy",  # Added label for creative self-efficacy
  "Perceived\n Cognitive\nWorkload",  # Combined label
  "Elaboration Depth"
)

# Calculate group means for each bot type and UX measure
# Standardized bot order for all graphics: Question-mode, Suggestion-mode, Model-led, Vanilla, Control
bot_order <- c("feedback", "suggestion", "improvement", "vanilla", "control")

# First calculate the regular UX measures
ux_spider_data <- data_clean %>%
  # Only include bot types that have UX measures (exclude control group)
  filter(bot_type %in% bot_order & bot_type != "control") %>%
  group_by(bot_type) %>%
  summarise(
    Performance_Expectancy = mean(Performance_Expectancy, na.rm = TRUE),
    Effort_Expectancy = mean(Effort_Expectancy, na.rm = TRUE),
    Hedonic_Motivation = mean(Hedonic_Motivation, na.rm = TRUE),
    Perceived_Ownership = mean(Perceived_Ownership, na.rm = TRUE),
    Creative_Self_Efficacy = mean(Creative_Self_Efficacy, na.rm = TRUE),  # Added creative self-efficacy
    NASA_TLX = mean(NASA_TLX, na.rm = TRUE),  # Added NASA_TLX for Mental Load
    .groups = "drop"
  )

# Now add elaboration depth from the data
elaboration_means <- elaboration_clean %>%
  group_by(bot_type_elab) %>%
  summarise(Elaboration_Depth = mean(H_IDEA_Score, na.rm = TRUE), .groups = "drop") %>%
  rename(bot_type = bot_type_elab)

# Merge elaboration data with UX data
ux_spider_data <- ux_spider_data %>%
  left_join(elaboration_means, by = "bot_type") %>%
  # Remove rows with all NA values
  filter(!is.na(Performance_Expectancy) | !is.na(NASA_TLX)) %>%
  # Ensure the order is correct so suggestion is plotted last
  arrange(match(bot_type, bot_order))

cat("Final UX spider data with real elaboration scores:\n")
print(ux_spider_data)

print("UX Spider plot data:")
print(ux_spider_data)

# Transform all measures to consistent 1-7 scale for better interpretation
# 7-point scales (1-7) -> keep as is
# tlx1 & tlx2 (0-100) -> transform to 1-7 scale  
# H_IDEA_Score (1-5) -> transform to 1-7 scale

cat("Original H_IDEA_Score (Elaboration_Depth) values by bot type:\n")
print(ux_spider_data %>% select(bot_type, Elaboration_Depth))

ux_spider_normalized <- ux_spider_data %>%
  mutate(
    # Keep 7-point scales as is (1-7)
    Performance_Expectancy = Performance_Expectancy,
    Effort_Expectancy = Effort_Expectancy,
    Hedonic_Motivation = Hedonic_Motivation,
    Perceived_Ownership = Perceived_Ownership,
    Creative_Self_Efficacy = Creative_Self_Efficacy,  # Added - keep as is (1-7 scale)
    
    # Transform 5-point scale (1-5) to 7-point scale (1-7) for H_IDEA_Score
    Elaboration_Depth = 1 + ((Elaboration_Depth - 1) / 4) * 6,  # Maps 1→1, 5→7
    
    # Transform NASA-TLX to 1-7 scale and rename to Mental_Load for spider plot
    Mental_Load = 1 + (NASA_TLX / 100) * 6  # Maps 0→1, 100→7 (NASA-TLX Mental Load)
  )

cat("Transformed values (all on 1-7 scale):\n")
print(ux_spider_normalized)

# Prepare final data for radarchart (fmsb format)
ux_radar_data <- ux_spider_normalized %>%
  select(all_of(ux_measures)) %>%
  as.data.frame()

# Set column names to readable labels
colnames(ux_radar_data) <- ux_measure_labels

# Add max and min rows (required by fmsb) - now using 1-7 scale
max_row <- rep(7, ncol(ux_radar_data))
min_row <- rep(1, ncol(ux_radar_data))

ux_radar_final <- rbind(max_row, min_row, ux_radar_data)

# Create bot labels using existing label_map
present_bot_types <- as.character(ux_spider_normalized$bot_type)
ux_bot_labels <- sapply(present_bot_types, function(x) {
  # Use single-line labels for spider plot
  label <- label_map[x]
  if(is.na(label)) label <- x
  # Return label as-is (no line breaks to remove)
  label
})

# Set row names
rownames(ux_radar_final) <- c("Max", "Min", ux_bot_labels)

print("Final UX radar data for plotting:")
print(ux_radar_final)

# Use original bot_colors palette for publication consistency
ux_radar_colors <- sapply(present_bot_types, function(x) {
  color_hex <- bot_colors[x]
  if(is.na(color_hex)) color_hex <- "#808080"  # Default gray
  # Convert to RGB with professional transparency for CHI publication
  rgb_vals <- col2rgb(color_hex)
  rgb(rgb_vals[1], rgb_vals[2], rgb_vals[3], alpha = 70, maxColorValue = 255)
})

ux_radar_border_colors <- sapply(present_bot_types, function(x) {
  color_hex <- bot_colors[x]
  if(is.na(color_hex)) color_hex <- "#808080"
  color_hex
})

print("Bot types for UX spider plot:")
print(present_bot_types)
print("UX Legend labels:")
print(ux_bot_labels)

# Set up the plot area
par(mar = c(2, 2, 2, 2), mfrow = c(1, 1))

# Create radar chart with CHI publication styling
radarchart(
  ux_radar_final,
  # Axis settings
  axistype = 1,
  maxmin = TRUE,
  
  # Grid settings (professional, subtle)
  cglcol = "grey80",
  cglty = 1,
  cglwd = 0.8,
  
  # Axis labels (1-7 scale)
  axislabcol = "grey10",
  caxislabels = seq(1, 7, 1),
  calcex = 1.0,
  
  # Polygon settings (professional colors and line weights)
  pcol = ux_radar_border_colors,
  pfcol = ux_radar_colors,
  plwd = 2.5,  # Professional line weight
  plty = 1,
  
  # Variable label settings (publication appropriate)
  vlcex = 1.1,
  vlabels = colnames(ux_radar_final),
  
  # Grid segments for 1-7 scale (6 segments for 7 labels)
  seg = 6
)

# Add professional legend for CHI - positioned to avoid overlap with labels
legend(
  x = 0.8, y = 1.25,
  legend = ux_bot_labels,
  bty = "n",
  pch = 15,  # Square symbols for better printing
  col = ux_radar_border_colors,
  text.col = "black",
  cex = 1.0,
  pt.cex = 1.8,
  title = "Condition",
  title.col = "black",
  title.cex = 1.0
)

# Also create PDF version  (vector graphics for LaTeX)
pdf(fig_path("ux_measures_spider_chart.pdf"), width = 10, height = 8, useDingbats = FALSE)

par(mar = c(2, 2, 2, 2), mfrow = c(1, 1))

radarchart(
  ux_radar_final,
  axistype = 1,
  maxmin = TRUE,
  cglcol = "grey80",
  cglty = 1,
  cglwd = 0.8,
  axislabcol = "grey10",
  caxislabels = seq(1, 7, 1),
  calcex = 1.0,
  pcol = ux_radar_border_colors,
  pfcol = ux_radar_colors,
  plwd = 2.5,
  plty = 1,
  vlcex = 1.1,
  vlabels = colnames(ux_radar_final),
  seg = 6
)

legend(
  x = 0.8, y = 1.25,
  legend = ux_bot_labels,
  bty = "n",
  pch = 15,
  col = ux_radar_border_colors,
  text.col = "black",
  cex = 1.0,
  pt.cex = 1.8,
  title = "Condition",
  title.col = "black",
  title.cex = 1.0
)

dev.off()
```
